---
title: "Show B0 and B1 are unbiased"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```



### Perform some simulations to empirically show that beta0 and beta1 are unbiased. In particular, do the following:
#### (i) Randomly sample 75 values of X from N(10, 12).
#### (ii) Randomly sample 75 values of Y from N(15 + 2X, 42). (Note: If you plug in your vector X of 75 values into rnorm with n=75, that will sample a corresponding Y to go with each of the X values).
#### (iii) Run a regression of Y over X and save the values of beta0 and beta1.
#### (iv) Repeat this 10000 times.

```{r, message=FALSE, warning=FALSE}
beta0 <- NULL
beta1 <- NULL

for(i in 1:10000){
  x_vals <- rnorm(75, mean=10, sd=1)
  y_vals <- rnorm(75, mean=(15+2*x_vals), 4)
  
  data_frame <- data.frame(x_vals, y_vals)
  
  model <- lm(y_vals ~ x_vals, data = data_frame)
  bt0 <- model[["coefficients"]][["(Intercept)"]]
  bt1 <- model[["coefficients"]][["x_vals"]]
  
  beta0 <- c(beta0, bt0)
  beta1 <- c(beta1, bt1)
}


```

#### (v) Calculate the mean of all the beta0 and beta1 values.
```{r ,message=FALSE, warning=FALSE}
  beta0_mean <- mean(beta0)
  beta1_mean <- mean(beta1)
```
```{r, message=FALSE, warning=FALSE}
  beta0_mean
```
```{r, message=FALSE, warning=FALSE}
  beta1_mean
```
#### (vi) Compare the empirical means from part v to the true values of beta0 and beta1.
They are relatively the same. We obtained Y randomly from a distribution N(15 + 2X, 42). As such, we expected the y-intercept to be 15 on average and beta1 to be 2 on average. Here, we got that are almost exactly similar to what we expected as is evident above.With a larger sample, these values are expected to be closer to 15 and 2, respectively

#### (v) Make histograms of the 10000 values of ˆ 0 and ˆ 1, and overlay a red vertical line on each at the true parameter value.

##### Beta0
```{r}
 hist(beta0)
abline(v=15, col='red', lwd=3,)
```

##### Beta1
```{r}
hist(beta1)
abline(v=2, col='red', lwd=3,)
```
